Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-11 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
Section IV.C (added comment)

The parameter inference in this paper follows configurations identical to the
ones used on these events for the \textsc{pSEOBNRv4HM} analysis in
Ref.~\cite{LIGOScientific:2021sio}. GW150914 was a 2-detector  (HL) event while
GW200129 was 3-detector (HLV).
%
We consequently use the same strain data $h(t)$, detector
power-spectral-densities $S_n(f)$ and calibration envelopes as were used for
the analyses in Ref.~\cite{LIGOScientific:2021sio}.
%
%The only difference between the sampling configurations is that we do not
%sample over the fractional deviations in the $(220)$ QNM frequencies and
%damping times, but instead on $\ell$ while holding $\{\delta \omega_k^{(j)}\},$
%and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions, summarized
%in Table~\ref{tab:ref_theories_qnms}.
%
\sout{In Fig.~\ref{fig:corner_plot}, we show the final spin $\chi_f$ and
detector-frame remnant mass $(1 + z) M_f$ for GW150914 for GR and the
illustrative case of dCS gravity. We see that our waveform models does not
introduce a substantial change to the GR estimates on this parameters, as
required by the ParSpec expansion (see discussion in
Sec.~\ref{sec:review_parspec}).}\agcomm{This reference to Fig.2 appears misplaced here. IMO, Fig 2. has two purposes. 1) to show that we do not need the high-spin version of the fits Carullo used, because our spin posteriors are well-localised around 0.7, and 2) to assure the reader that we were right in using the GR values of the final mass and spin in the ParSpec expansion, because introducing nonGR parameters has not ended up biasing our estimates of Mf-chif.  I think those are the points at which we need to refer to this figure.}
%
In Sec.~\ref{sec:results}, we will enumerate through the different theories and
outline the highlight results. Whenever possible, we also combine results from
multiple events to obtain the strongest possible bound on $\ell$.

>>>>

The parameter inference in this paper follows configurations identical to the
ones used on these events for the \textsc{pSEOBNRv4HM} analysis in
Ref.~\cite{LIGOScientific:2021sio}. GW150914 was a 2-detector  (HL) event while
GW200129 was 3-detector (HLV).
%
We consequently use the same strain data $h(t)$, detector
power-spectral-densities $S_n(f)$ and calibration envelopes as were used for
the analyses in Ref.~\cite{LIGOScientific:2021sio}.
%
%The only difference between the sampling configurations is that we do not
%sample over the fractional deviations in the $(220)$ QNM frequencies and
%damping times, but instead on $\ell$ while holding $\{\delta \omega_k^{(j)}\},$
%and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions, summarized
%in Table~\ref{tab:ref_theories_qnms}.
%
\sout{In Fig.~\ref{fig:corner_plot}, we show the final spin $\chi_f$ and
detector-frame remnant mass $(1 + z) M_f$ for GW150914 for GR and the
illustrative case of dCS gravity. We see that our waveform models does not
introduce a substantial change to the GR estimates on this parameters, as
required by the ParSpec expansion (see discussion in
Sec.~\ref{sec:review_parspec}).}\agcomm{This reference to Fig.2 appears misplaced here. IMO, Fig 2. has two purposes. 1) to show that we do not need the high-spin version of the fits Carullo used, because our spin posteriors are well-localised around 0.7, and 2) to assure the reader that we were right in using the GR values of the final mass and spin in the ParSpec expansion, because introducing nonGR parameters has not ended up biasing our estimates of Mf-chif.  I think both of these points can be addressed in the discussions section. That is also where we can put the other corner plot with the remaining intrinsic parameters. One side-advantage of this is that the figures would then also appear slightly later in the paper, as we had originally planned.}
%
In Sec.~\ref{sec:results}, we will enumerate through the different theories and
outline the highlight results. Whenever possible, we also combine results from
multiple events to obtain the strongest possible bound on $\ell$.
